### 2015-09-10 Irregular-occ/Irregular-occ.tex
.

\begin{table}
\caption{\label{Tab: satellite-diameter} Estimated diameter of the satellites and correspondent apparent diameter}
\begin{centering}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & km  & mas\tablefootmark{a} & References \tabularnewline
\hline
Ananke & 29 &  & 1 \tabularnewline
Carme & 46 &  & 1 \tabularnewline
Elara & 86 &  & 1 \tabularnewline
Himalia & $(150 \pm 20) \times (120\pm 20)$ &  & 2 \tabularnewline
Lysithea & 36 &  & 1 \tabularnewline
Pasiphae & 62 & & 1 \tabularnewline
Sinope & 37 & & 1 \tabularnewline
\hdashline
Phoebe & $212 \pm 1.4$ & & 3 \tabularnewline
\hdashline
Nereid & $340 \pm 50$ &  & 4 \tabularnewline
Triton & $2707 \pm 2.0$ &  & 5 \tabularnewline
\hline
\end{tabular}
\tablebib{
(1) \cite{Rettig2001}; (2) \cite{Porco2003}; (3) \cite{Thomas2010}; (4) \cite{Thomas1991} (5) \cite{Thomas2000}.}
\end{centering}
\tablefoottext{a}{Using a mean distance from Jupiter of XX AU, from Saturn of XX AU and from Neptune of XX AU.}
\par
\end{table}

@@

\begin{table}
\caption{\label{Tab: comparison-Himalia} Comparison between the predictions of the Himalia occultation at March 03, 2015. \textcolor{red}{Ainda vou terminar de preencher a tabela e tem que ver direito o offset do ajuste}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A   \tabularnewline
\hline
Nominal & 00:39:25 UTC & $0\farcs714$ \tabularnewline
Offset &   & \tabularnewline
Feb. 22 Obs. & +12s & -33mas (109km) \tabularnewline
Mar. 03 Obs. & -10s & -19mas (61km)\tabularnewline
\hline
\end{tabular}
\par\end{centering}

@@

\begin{table}
\caption{\label{Tab: comparison-Elara} Comparison between the predictions of Elara occultation at March 30, 2015. \textcolor{red}{Ainda vou terminar de preencher a tabela e tem que ver direito o offset do ajuste}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A  \tabularnewline
\hline
Nominal & 01:45:15 UTC & $1\farcs139$ \tabularnewline
Offset &  & \tabularnewline
Mar. 25 Obs. & -59 s & -17mas (61km) \tabularnewline
Apr. 02 Obs. & +15 s & -89mas (307km) \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\end{table}

@@

The candidate stars was searched in the UCAC4 catalogue, except for the candidates in 2015 and 2016 for Triton and Nereid. In this case, we used the WFI catalogue that was generated from observations made with ESO2p2/WFI CCD mosaic that covered the path of Neptune in the sky-plane up to 2016.

In table \ref{Tab: satellite-occultation} it's presented the number of stellar occultations predicted by year for each satellite.

\begin{table}
\caption{\label{Tab: satellite-occultation} Number of stellar occultations for each satellite from 2015 up to 2017}
\begin{centering}
\begin{tabular}{lcccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & 2015  & 2016 & 2017 & Total \tabularnewline
\hline
Ananke &  &  & & \tabularnewline
Carme &  &  &  & \tabularnewline
Elara &  &  &  & \tabularnewline
Himalia &  &  &  & \tabularnewline
Lysithea &  &  &  & \tabularnewline
Pasiphae &  & &  & \tabularnewline
Sinope &  &  &  & \tabularnewline
\hdashline
Phoebe & 13 & 22 & 98 & 133\tabularnewline
\hdashline
Nereid & 40 & 11 & 1 & 52 \tabularnewline
Triton &  &  &  & \tabularnewline
\hline
\end{tabular}
\par \end{centering}
\end{table}

>>>>

\begin{table}
\caption{\label{Tab: satellite-diameter} Estimated diameter of the satellites and correspondent apparent diameter}
\begin{centering}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & km  & mas\tablefootmark{a} & References \tabularnewline
\hline
Ananke & 29 & 8 & 1 \tabularnewline
Carme & 46 & 13 & 1 \tabularnewline
Elara & 86 & 24 & 1 \tabularnewline
Himalia & $(150\times120) \pm 20$\tablefootmark{b} & 41 & 2 \tabularnewline
Lysithea & 36 & 10 & 1 \tabularnewline
Pasiphae & 62 & 17 & 1 \tabularnewline
Sinope & 37 & 10 & 1 \tabularnewline
\hdashline
Phoebe & $212 \pm 1.4$\tablefootmark{b} & 32 & 3 \tabularnewline
\hdashline
Nereid & $340 \pm 50$\tablefootmark{c} & 15 & 4 \tabularnewline
Triton & $2707 \pm 2.0$\tablefootmark{c} & 124 & 5 \tabularnewline
\hline
\end{tabular}
\tablebib{
(1) \cite{Rettig2001}; (2) \cite{Porco2003}; (3) \cite{Thomas2010}; (4) \cite{Thomas1991}; (5) \cite{Thomas2000}.}
\end{centering}
\tablefoottext{a}{Using a mean distance from Jupiter of 5 AU, from Saturn of 9 AU and from Neptune of 30 AU.}
\tablefoottext{b}{From Cassini observation.}
\tablefoottext{c}{From Voyager-2 observation.}
\par
\end{table}

@@

\begin{table}
\caption{\label{Tab: comparison-Himalia} Comparison between the predictions of the Himalia occultation at March 03, 2015. \textcolor{red}{Tem que ver direito o offset do ajuste}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A   \tabularnewline
\hline
Nominal & 00:39:25 UTC & $0\farcs714$ \tabularnewline
Offset &   & \tabularnewline
Feb. 22 Obs. & +12s & -33mas (109km) \tabularnewline
Mar. 03 Obs. & -10s & -19mas (61km)\tabularnewline
\hline
\end{tabular}
\par\end{centering}

@@

\begin{table}
\caption{\label{Tab: comparison-Elara} Comparison between the predictions of Elara occultation at March 30, 2015. \textcolor{red}{Tem que ver direito o offset do ajuste}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A  \tabularnewline
\hline
Nominal & 01:45:15 UTC & $1\farcs139$ \tabularnewline
Offset &  & \tabularnewline
Mar. 25 Obs. & -59 s & -17mas (61km) \tabularnewline
Apr. 02 Obs. & +15 s & -89mas (307km) \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\end{table}

@@

The candidate stars was searched in the UCAC4 catalogue, except for the candidates in 2015 and 2016 for Triton and Nereid. In this case, we used the WFI catalogue that was generated from observations made with ESO2p2/WFI CCD mosaic that covered the path of Neptune in the sky-plane up to 2016 (see Sec. \ref{Sec: predictions}).

A total of \textcolor{red}{588} events were detected to happen between and the period presented. In table \ref{Tab: satellite-occultation} it's presented the number of stellar occultations predicted by year for each satellite.

\begin{table}
\caption{\label{Tab: satellite-occultation} Number of stellar occultations for each satellite from 2015 up to 2017.}
\begin{centering}
\begin{tabular}{lcccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & 2015  & 2016 & 2017 & Total \tabularnewline
\hline
Ananke & 22 & 12 & 16 & 50 \tabularnewline
Carme & 25 & 20 & 14 & 59 \tabularnewline
Elara & 32 & 14 & 16 & 62 \tabularnewline
Himalia & 25 & 15 & 12 & 52 \tabularnewline
Lysithea & 22 & 16 & 11 & 49 \tabularnewline
Pasiphae & 26 & 19 & 20 & 65 \tabularnewline
Sinope & 19 & 15 & 21 & 55 \tabularnewline
\hdashline
Phoebe & 13 & 32 & 98 & 143 \tabularnewline
\hdashline
Nereid & 41 & 11 & 1 & 53 \tabularnewline
Triton &  &  &  &  \tabularnewline
\hline
\end{tabular}
\par \end{centering}
Occultations predicted using the UCAC4 catalogue. For Nereid and Triton, the occultations in 2015 and 2016 were predicted using the WFI catalogue as explained in Sec. \ref{Sec: predictions}.
\end{table}

Concerning the UCAC4 stars, an accuracy of about 20-50 mas in the star position would give a 15-40\% probability of observe such an event by Ananke, the smallest irregular satellite in the sample. For Himalia, the occultation would have 80-100\% probability. Combined with a mean accuracy in the position of 30 mas for Himalia and 100 mas for Ananke mas published in Table 2 of \cite{Jacobson2012}, the probability of success would be around 50-80\% for Himalia and $\approx$5\% for Ananke. Observations a few days before the date of occultation predicted may diminish the combined accuracy to 40-80 mas, depending on the magnitude of the objects.

The tests made with an occultation expected to happen in March 03, 2015 for Himalia showed that this event could probably be observed in case there were observers available in the shadow area. Fig. \ref{Fig: occ-Himalia} show the maps made for 4 different offset corrections as explained in Sec. \ref{Sec: testes}. Table \ref{Tab: comparison-Himalia} show numerically the difference between the maps. A similar test was made for an occultation of Elara in March 30, 2015. The difference between the maps can be seen summarized in Table \ref{Tab: comparison-Elara}.

Continuous observations of the satellites and candidates are recommended and new numerical integrations of the orbits of the satellites are expected to reduce the respective position errors. The GAIA catalogue, which are to be released in mid-2016 will improve the position error of the stars and occultations of fainter stars not present in the UCAC4 catalogue may be found as candidates. Consequently, the astrometry of the satellites with the GAIA catalogue will improve the position errors of the satellites that will allow for better predictions and a bigger probability of observe stellar occultations by irregular satellites.
